---
title: "Fauna monitoring report"
author: "Pacioni C."
output: 
  word_document:
          fig_caption: true
          fig_width: 7
---
```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE, error=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, error=FALSE)
time <- format(Sys.time(), "%d %B %Y")

library(WPdata, quietly = TRUE)
library(data.table, quietly = TRUE)
library(ggplot2)
dir.in <- "C:\\Users\\30373314\\Documents\\Woylie\\Genetics\\DNA analysis\\Whiteman Park\\DB"
nfile="Woodland Reserve Fauna Data.xlsx"
sheet="DB"
data <- (read.trapping(dir.in, last.row=125, nfile="Sample_data.xlsx"))
data <- data.table(data)
nspecies <- length(data[, unique(Species)])
```

This is a provisional report on native fauna monitoring in the Woodland reserve 
at Whiteman Park as for `r time`. At establishment, only woylies 
(_Bettongia penicillata ogylbyi_) and quendas (_scientific name_) were present in 
the reserve. However, since  its establishment, **date**, a total of `r nspecies`  
species are now introduced and several surveys were carried out to monitor the 
status  of the Woodland reserve fauna as detailed in
**Table 1**.







```{r}
nsessions <- trap.year(data)
knitr::kable(nsessions, caption="**Table 1.** Total number of trapping sessions for 
             each year, for each species monitored in the Woodland reserve at Whiteman Park.")
```



As part of the standard monitoring, several demographic and morphological parameters 
have been recorded. These allow for a monitoring of population condition over time 
as exemplified by the following plots:

```{r results='hide'}
p <- params.plot(data, params=c("Animal.Weight", "Pes"), species="Woylie")
```



```{r fig.cap="**Figure 1.** Plot of mean animal weight within each trapping session"}

print(p[[1]] + ylab("Weight (kg)"))

```



```{r fig.cap="**Figure 2.** Plot of mean pes length within each trapping session"}

print(p[[2]] + ylab("Pes (mm)"))

```
